### 2024-11-02 project1/nsSurvey.tex
new

Figure~\ref{fig1:c_model} illustrates the computational time of implementing different nested simulation procedures for the portfolio of geometric Asian options with $d = 10$.
The simulation time is omitted as it is the same for all procedures.
The remaining computations can be decomposed into two parts: hyperparameter tuning and model implementation.
The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the metamodels, and the model implementation cost is the cost of fitting the metamodels and generating predictions from the trained metamodels.
For each procedure, each point in Figure~\ref{fig1:c_model} represents the average computational time for a given simulation budget $\Gamma$.
A regression model is fitted to each model respectively, and its slope can be viewed as the growth rate of the computational time with respect to $\Gamma$.
The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
This cost does not grow with the simulation budget $\Gamma$, as its slope is close to $0$.
The regression-based procedure does not require hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
The slope of the regression line is close to $1$, resembling the its algorithmic complexity in Table~\ref{tab1:complexity}.
The kernel smoothing-based and KRR-based procedure requires cross-validation to estimate the optimal hyperparameters.
In our implementaion of kNN, the cross-validation is conducted using a grid search with a search space whose cardinality does not grow with the simulation budget $\Gamma$.
However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
The KRR-based procedure requires Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space grows with the simulation budget $\Gamma$.
The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity in Table~\ref{tab1:complexity}.
The efficient implementation of KRR is an active area of research, and the computational cost of KRR can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
Our observation for KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported quickly increasing with the number of samples.
The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$. 
In summary, for a large simulation budget, the regression-based procedure is the most efficient among all metamodel-based procedures in terms of computational time.

\section{Conclusion} \label{sec1:conclusion}
In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodels. 
In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different metamodels using the same set of numerical examples. 
Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding metamodels.
To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
With extensive numerical experiments, we have found the finite-sample performance of a procedure can deviate from its theory. 
In theory, supervised learning-based nested simulation procedures often provide higher rates of convergence, but they come at the computational expense of model training and generating predictions from the trained models. 
The likelihood ratio-based procedure requires no training, but it is computationally expensive to compute and store the likelihood weights.
As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
A kernel-based procedure, e.g., kNN and KRR, requires cross-validation, and its empirical performance depends heavily the choice of hyperparameters.
A kNN-based procedure is sensitive to the asset dimension and the problem complexity.
A KRR-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
For kernel-based procedures, the computational cost is heavily dependent on the efficient implementation of the associated algorithms.
For a nested estimation problem with a given computational budget, we suggest the use of the regression-based simulation procedure when the budget size is moderate. 
It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for option portfolios. 
However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
For payoff functions with high complexity or high dimensionality, the regression-based procedure may not be the best choice.
In practice, a variable annuity contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
In Chapter~\ref{chap:project2}, we will examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.

>>>>

Figure~\ref{fig1:c_model} illustrates the computational time of implementing different nested simulation procedures for the portfolio of geometric Asian options with $d = 10$.
The simulation time is omitted as it is the same for all procedures.
The remaining computations can be decomposed into two parts: hyperparameter tuning and model implementation.
The hyperparameter tuning cost is the cost of estimating the optimal hyperparameters for the metamodels, and the model implementation cost is the cost of fitting the metamodels and generating predictions from the trained metamodels.
For each procedure, each point in Figure~\ref{fig1:c_model} represents the average computational time for a given simulation budget $\Gamma$.
A regression model is fitted to each model respectively, and its slope can be viewed as the growth rate of the computational time with respect to $\Gamma$.
\begin{itemize}
    \item The total computational time of the standard procedure is mostly attributed to finding the optimal $M$ and $N$ using the bootstrap-based budget allocation strategy from~\cite{zhang2021bootstrap}.
    This cost does not grow with the simulation budget $\Gamma$, as its slope is close to $0$.
    \item The regression-based procedure does not require hyperparameter tuning, and its total computational time is mainly attributed to the model implementation.
    The slope of the regression line is close to $1$, resembling the its algorithmic complexity in Table~\ref{tab1:complexity}.
    \item The kernel smoothing-based and KRR-based procedure requires cross-validation to estimate the optimal hyperparameters. 
    In our implementaion of kNN, the cross-validation is conducted using a grid search with a search space whose cardinality does not grow with the simulation budget $\Gamma$.
    However, the cross-validation cost of the kernel smoothing-based procedure grows with the simulation budget $\Gamma$ as more samples are involved.
    The KRR-based procedure requires Bayesian optimization to estimate the optimal hyperparameters, and the cardinality of the search space also grows with the simulation budget $\Gamma$.
    The empirical cost of the KRR-based procedure does not resemble its algorithmic complexity in Table~\ref{tab1:complexity}.
    The efficient implementation of KRR is an active area of research, and the computational cost of KRR can be reduced by using a low-rank approximation of the kernel matrix, e.g., the Nystr\"om method~\citep{nystrom1930praktische}.
    Our observation for KRR implementation time is in line with the findings in~\cite{scikit-learn}, where the cost of KRR is reported quickly increasing with the number of samples.
    \item The likelihood ratio-based procedure requires no hyperparameter tuning, and its total computational time is mainly attributed to the likelihood weight calculation, which is $\mathcal{O}(M^2)$. 
\end{itemize}
In summary, for a large simulation budget, the regression-based procedure is the most efficient among all metamodel-based procedures in terms of computational time.
For moderate simulation budgets, the regression-based procedure should be the preferred choice.

\section{Conclusion and Extensions} \label{sec1:conclusion}
In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a metamodels. 
In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different metamodels using the same set of numerical examples. 
Asymptotic properties of estimators for different nested simulation procedures are influenced by their corresponding metamodels.
To show an asymptotic convergence result, a more complex metamodels requires a more stringent set of assumptions on the distribution of the outer scenario and the inner simulation noise.
With extensive numerical experiments, we have found the finite-sample performance of a procedure can deviate from its theory. 
In theory, supervised learning-based nested simulation procedures often provide higher rates of convergence, but they come at the computational expense of model training and generating predictions from the trained models. 
The likelihood ratio-based procedure requires no training, but it is computationally expensive to compute and store the likelihood weights.
As a result, the total computational budget is not necessarily the same as the simulation budget, which is usually a limiting factor for practical applications.
A kernel-based procedure, e.g., kNN and KRR, requires cross-validation, and its empirical performance depends heavily the choice of hyperparameters.
A kNN-based procedure is sensitive to the asset dimension and the problem complexity.
A KRR-based procedure is computationally expensive, and its cost grows quickly with the simulation budget.
For kernel-based procedures, the computational cost is heavily dependent on the efficient implementation of the associated algorithms.
For a nested estimation problem with a given computational budget, we suggest the use of the regression-based simulation procedure when the budget size is moderate. 
It is efficient to implement, and it exhibits fast empirical convergence in estimating risk measures for option portfolios. 
However, we have only examined the performance for option portfolios in this study, where finding a suitable set of basis functions for regression is relatively easy.
In practice, a variable annuity contract is often high-dimensional in time with a complex payoff structure, and it is a challenging problem for nested simulation procedures.
The time dependence in the feature space leads to multi-collinearity, and the regression-based procedure may not be the best choice.
In such cases, a neural network-based procedure may be more suitable, as it is a data-driven algorithm that finds a suitable set of basis functions automatically.
In Chapter~\ref{chap:project2}, we examine the performance of regression-based and neural network-based nested simulation procedures for estimating risk measures for variable annuities.

### 2024-11-02 project2/nnMetamodels.tex
new

We are curious about fundamental questions like ``What do DNNs learn from noisy data?'' and ``How well do neural networks learn from noisy data?''.
Data-driven answers to these questions prevail in the existing literature.
In supervised learning, DNNs are believed to learn from the given data about the feature-label relationship to predict new labels for unseen features.
Cross validation using to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
Generalization error on the test labels is another popular assessment metric.
But the test set is also a subset of the original data.
In this study, we revisit these questions in a simulation context and propose an alternative approach to answer them.
Instead of relying solely on real-data (splitting it into multiple subsets), we propose using stochastic simulation outputs as training labels for DNNs.
By controlling the simulation design parameters, such as the number of independent replications, we can control the quality and also the quantity of the training labels fed into the neural networks.
In such a controlled environment, we obtain more clear-cut answers to the above fundamental questions.

In nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as the inner simulation model.
Borrowing terminologies from machine learning research, we can view a set of simulated outer scenarios and the estimated hedging errors for those scenarios as the \textit{features} and noisy \textit{labels}.
The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
One can train supervised learning models using these simulated features and labels.
They are then used to replace the time-consuming inner simulations by the trained model.
We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in simulation literature.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using DNNs as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use DNNs as metamodels of a simulation model for structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the Conditional Value-at-Risk (CVaR) of a portfolio of derivative securities, and~\cite{gan2015valuation} use stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use regression, kernel smoothing, and the likelihood ratio method, respectively.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical VA contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of DNN models in predicting the noiseless labels.
\end{enumerate}

@@

In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of variable annuities.
A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.

@@

Variable annuity contracts offer different types of guarantees.
Generally speaking, a portion of the VA premium is invested in a sub-account whose return is linked to some stock indices.

@@

Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
Denote the policyholder's (random) time of death by $\tau>0$.
Then the contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents the incurred investment expenses.

@@

% For example, for GMWB, a standard nested simulation procedure to estimate the $\alpha$-CVaR of $L$ is as follows:
% \begin{enumerate}
%     \item For $i=1,\ldots,M$, simulate outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$ under the real-world measure $\mathbb{P}$.
%     Figure~\ref{fig2:illustration} illustrates the inner simulation experiments needed for an outer scenario.

%     \item For $t=0$, simulate time-$0$ inner paths $\bStilde_{0}^{(j)} = (\Stilde_{1}^{(j)},\Stilde_{2}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $V_0$ by $\Vhat_0 = \sum_{s=1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s]$ and estimate $\Deltahat_0 = \Delta_0(\Stilde_{1}^{(j)},\ldots,\Stilde_{T}^{(j)} | S_0)$ based on~\eqref{eq2:delta}.
%     Note that $S_0$ is known, so these inner paths do not depend on any outer scenario.
%     The same $\Vhat_0$ and $\Deltahat_0$ are used in all scenarios.

%     \item Given each scenario $\bS^{(i)}$, the following inner simulation is needed to estimate the corresponding loss $\Lhat_i$ for that scenario.
%     \begin{enumerate}
%         \item At each time~$t=1,\ldots,T-1$, simulate inner paths $\bStilde_{t}^{(ij)} = (\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)})$, $j=1,\ldots,N$ under $\mathbb{Q}$ {and} then estimate $\Delta_t$ by $\Deltahat_t^{(i)} = \Delta_t(\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)} | \bm{S}_t^{(i)})$ based on~\eqref{eq2:delta}.

%         \item Use scenarios $\bS^{(i)}$ and $\Vhat_0$ and $\Deltahat_t^{(i)}$ to calculate losses $\Lhat_i^{MC}$, $t=0,\ldots,T-1$, based on~\eqref{eq2:lossrv}. Then sort them as $\Lhat^{MC}_{(1)}\leq \Lhat^{MC}_{(2)} \leq \cdots\leq \Lhat^{MC}_{(M)}$.
%     \end{enumerate}

%     \item Estimate $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{MC}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{MC} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{MC}}\Lhat_{i}^{MC}$
%     where $\widehat{\tail}_{k}^{MC}$ denotes a \textit{Monte Carlo tail scenario set} associated with the largest $k$ estimated losses.
% \end{enumerate}

>>>>

We are curious about fundamental questions like ``What do DNNs learn from noisy data?'' and ``How well do neural networks learn from noisy data?''.
Data-driven answers to these questions prevail in the existing literature.
In supervised learning, DNNs are believed to learn from the given data about the feature-label relationship to predict new labels for unseen features.
Cross-validation using to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
Generalization error on the test labels is another popular assessment metric.
However, the test set is also a subset of the original data.
In this study, we revisit these questions in a simulation context and propose an alternative approach to answer them.
Instead of relying solely on real-data and splitting it into multiple subsets, we propose using stochastic simulation outputs as training labels for DNNs.
By controlling the simulation design parameters, such as the number of independent replications, we can control the quality and also the quantity of the training labels fed into the neural networks.
In such a controlled environment, we obtain more clear-cut answers to the above fundamental questions.

In nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as the inner simulation model.
Borrowing terminologies from machine learning research, we can view a set of simulated outer scenarios and the estimated hedging errors for those scenarios as the \textit{features} and noisy \textit{labels}.
The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
One can train supervised learning models using these simulated features and labels.
They are then used to replace the time-consuming inner simulations by the trained model.
We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in simulation literature.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using DNNs as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use DNNs as metamodels of a simulation model for structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the CVaR of a portfolio of derivative securities, and~\cite{gan2015valuation} use stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use regression, kernel smoothing, and the likelihood ratio method, respectively.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical VA contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of DNN models in predicting the noiseless labels.
\end{enumerate}

@@

In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of VAs.
A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.

@@

VA contracts offer different types of guarantees.
Generally speaking, a portion of the VA premium is invested in a sub-account whose return is linked to some stock indices.

@@

Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
Denote the policyholder's (random) time of death by $\tau>0$.
The contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents the incurred investment expenses.

@@
